---
title: "High Frequency Checks: Test of all functions template"
always_allow_html: yes
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output:
  rmarkdown::html_vignette:
    toc: yes
vignette: >
  \usepackage[utf8]{inputenc}
  %\VignetteIndexEntry{High Frequency Checks: Test of all functions template}
  %\VignetteEngine{knitr::rmarkdown}
geometry: margin=0.5in
fontsize: 10pt
editor_options: 
  chunk_output_type: inline
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(gsubfn)
library(dplyr)
library(data.table)
library(HighFrequencyChecks)
```
```{r surveysDataset, eval=TRUE, echo=FALSE}
dset<-list()
dset[["lev1"]]<-sample_dataset
```
```{r sampleSizeDataset, eval=TRUE, echo=FALSE}
begin_sample<-NA
sampleSizeTable<-SampleSize
```
```{r shapefiles, eval=TRUE, echo=FALSE}
begin_shp<-NA
adminBoundaries<-admin
sampledPoints<-SamplePts
```
```{r initializeVariables, eval=TRUE, echo=FALSE}
adminBoundariesSite<-"Union"
buffer<-10
consentForValidSurvey<-"yes"
dateFormat<-"%m/%d/%Y"
dates<-c("survey_start","end_survey")
dsCoordinates<-c("X_gps_reading_longitude","X_gps_reading_latitude")
dsSite<-"union_name"
enumeratorID<-"enumerator_id"
householdSize<-"consent_received.respondent_info.hh_size"
minimumSurveyDuration<-30
minimumSurveyDurationByIndividual<-10
otherPattern<-"_other$"
questionsEnumeratorIsLazy<-c(consent_received.shelter_nfi.non_food_items=3, consent_received.food_security.main_income=3, consent_received.child_protection.boy_risk=3, consent_received.child_protection.girl_risk=3)
questionsSurveyBigValues<-c(consent_received.food_security.spend_food=25000, consent_received.food_security.spend_medication=25000, consent_received.food_security.spend_education=25000, consent_received.food_security.spend_fix_shelter=25000, consent_received.food_security.spend_clothing=25000, consent_received.food_security.spend_hygiene=25000, consent_received.food_security.spend_fuel=25000, consent_received.food_security.spend_hh_items=25000, consent_received.food_security.spend_transport=25000, consent_received.food_security.spend_communication=25000, consent_received.food_security.spend_tobacco=25000, consent_received.food_security.spend_rent=25000, consent_received.food_security.spend_debts=25000, consent_received.food_security.spend_other=25000)
questionsSurveySmallValues<-c(consent_received.food_security.spend_food=25000, consent_received.food_security.spend_medication=25000, consent_received.food_security.spend_education=25000, consent_received.food_security.spend_fix_shelter=25000, consent_received.food_security.spend_clothing=25000, consent_received.food_security.spend_hygiene=25000, consent_received.food_security.spend_fuel=25000, consent_received.food_security.spend_hh_items=25000, consent_received.food_security.spend_transport=25000, consent_received.food_security.spend_communication=25000, consent_received.food_security.spend_tobacco=25000, consent_received.food_security.spend_rent=25000, consent_received.food_security.spend_debts=25000, consent_received.food_security.spend_other=25000)
sampleSizeTableAvailable<-"TotPts"
sampleSizeTableSite<-"Union"
sampleSizeTableTarget<-"SS"
startDataCollection<-"2018-11-11"
surveyConsent<-"survey_consent"
surveyDate<-"survey_date"
uniqueID<-"X_uuid"
deleteIsInterviewCompleted<-TRUE
deleteIsInterviewWithConsent<-TRUE
correctIsInterviewInTheCorrectSite<-TRUE
deleteIsInterviewAtTheSamplePoint<-TRUE
deleteIsUniqueIDMissing<-TRUE
deleteIsUniqueIDDuplicated<-TRUE
deleteIsSurveyOnMoreThanADay<-TRUE
deleteIsSurveyEndBeforeItStarts<-TRUE
deleteIsSurveyStartedBeforeTheAssessment<-TRUE
deleteIsSurveyMadeInTheFuture<-TRUE
deleteIsInterviewTooShort<-TRUE
deleteIsInterviewTooShortForTheHouseholdSize<-TRUE
```
```{r eval=TRUE, echo=FALSE}
dset[["lev1"]]$union_name<-tolower(dset[["lev1"]]$union_name)
```
```{r eval=TRUE, echo=FALSE}
sampleSizeTable$Union<-tolower(sampleSizeTable$Union)
```
```{r eval=TRUE, echo=FALSE}
adminBoundaries$Union<-tolower(adminBoundaries$Union)
```
```{r eval=TRUE, echo=FALSE}
options(scipen = 999)
```

## High Frequency Check - Examples

### isInterviewAtTheSamplePoint
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, dsCoordinates, sampledPoints, buffer, surveyConsent",
                                           names(dset)[stringi::stri_detect_fixed("lev1, dsCoordinates, sampledPoints, buffer, surveyConsent", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, dsCoordinates, sampledPoints, buffer, surveyConsent", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("isInterviewAtTheSamplePoint(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, dsCoordinates, sampledPoints, buffer, surveyConsent", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### isInterviewCompleted
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, surveyConsent, dates",
                                           names(dset)[stringi::stri_detect_fixed("lev1, surveyConsent, dates", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, surveyConsent, dates", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("isInterviewCompleted(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, surveyConsent, dates", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### isInterviewInTheCorrectSite
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, dsSite, dsCoordinates, adminBoundaries, adminBoundariesSite, surveyConsent",
                                           names(dset)[stringi::stri_detect_fixed("lev1, dsSite, dsCoordinates, adminBoundaries, adminBoundariesSite, surveyConsent", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, dsSite, dsCoordinates, adminBoundaries, adminBoundariesSite, surveyConsent", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("isInterviewInTheCorrectSite(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, dsSite, dsCoordinates, adminBoundaries, adminBoundariesSite, surveyConsent", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### isInterviewTooShort
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, surveyConsent, dates, minimumSurveyDuration",
                                           names(dset)[stringi::stri_detect_fixed("lev1, surveyConsent, dates, minimumSurveyDuration", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, surveyConsent, dates, minimumSurveyDuration", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("isInterviewTooShort(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, surveyConsent, dates, minimumSurveyDuration", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### isInterviewTooShortForTheHouseholdSize
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, surveyConsent, dates, householdSize, minimumSurveyDurationByIndividual",
                                           names(dset)[stringi::stri_detect_fixed("lev1, surveyConsent, dates, householdSize, minimumSurveyDurationByIndividual", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, surveyConsent, dates, householdSize, minimumSurveyDurationByIndividual", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("isInterviewTooShortForTheHouseholdSize(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, surveyConsent, dates, householdSize, minimumSurveyDurationByIndividual", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### isInterviewWithConsent
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, surveyConsent",
                                           names(dset)[stringi::stri_detect_fixed("lev1, surveyConsent", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, surveyConsent", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("isInterviewWithConsent(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, surveyConsent", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### isSurveyEndBeforeItStarts
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, surveyConsent, dates",
                                           names(dset)[stringi::stri_detect_fixed("lev1, surveyConsent, dates", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, surveyConsent, dates", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("isSurveyEndBeforeItStarts(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, surveyConsent, dates", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### isSurveyMadeInTheFuture
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, surveyConsent, dates",
                                           names(dset)[stringi::stri_detect_fixed("lev1, surveyConsent, dates", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, surveyConsent, dates", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("isSurveyMadeInTheFuture(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, surveyConsent, dates", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### isSurveyOnMoreThanADay
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, surveyConsent, dates",
                                           names(dset)[stringi::stri_detect_fixed("lev1, surveyConsent, dates", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, surveyConsent, dates", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("isSurveyOnMoreThanADay(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, surveyConsent, dates", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### isSurveyStartedBeforeTheAssessment
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, dates, surveyConsent, startDataCollection",
                                           names(dset)[stringi::stri_detect_fixed("lev1, dates, surveyConsent, startDataCollection", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, dates, surveyConsent, startDataCollection", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("isSurveyStartedBeforeTheAssessment(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, dates, surveyConsent, startDataCollection", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### isUniqueIDDuplicated
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, uniqueID, surveyConsent",
                                           names(dset)[stringi::stri_detect_fixed("lev1, uniqueID, surveyConsent", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, uniqueID, surveyConsent", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("isUniqueIDDuplicated(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, uniqueID, surveyConsent", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### isUniqueIDMissing
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, uniqueID, surveyConsent",
                                           names(dset)[stringi::stri_detect_fixed("lev1, uniqueID, surveyConsent", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, uniqueID, surveyConsent", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("isUniqueIDMissing(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, uniqueID, surveyConsent", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### assessmentDailyValidSurveys
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, surveyDate, dateFormat, surveyConsent",
                                           names(dset)[stringi::stri_detect_fixed("lev1, surveyDate, dateFormat, surveyConsent", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, surveyDate, dateFormat, surveyConsent", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("assessmentDailyValidSurveys(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, surveyDate, dateFormat, surveyConsent", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### assessmentDuration
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, dates",
                                           names(dset)[stringi::stri_detect_fixed("lev1, dates", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, dates", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("assessmentDuration(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, dates", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### assessmentDurationOutliers
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, dates",
                                           names(dset)[stringi::stri_detect_fixed("lev1, dates", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, dates", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("assessmentDurationOutliers(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, dates", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### assessmentProductivity
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, surveyDate, dateFormat, surveyConsent",
                                           names(dset)[stringi::stri_detect_fixed("lev1, surveyDate, dateFormat, surveyConsent", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, surveyDate, dateFormat, surveyConsent", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("assessmentProductivity(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, surveyDate, dateFormat, surveyConsent", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### assessmentTrackingSheet
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, dsSite, sampleSizeTable, sampleSizeTableSite, sampleSizeTableTarget, sampleSizeTableAvailable, surveyConsent, consentForValidSurvey",
                                           names(dset)[stringi::stri_detect_fixed("lev1, dsSite, sampleSizeTable, sampleSizeTableSite, sampleSizeTableTarget, sampleSizeTableAvailable, surveyConsent, consentForValidSurvey", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, dsSite, sampleSizeTable, sampleSizeTableSite, sampleSizeTableTarget, sampleSizeTableAvailable, surveyConsent, consentForValidSurvey", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("assessmentTrackingSheet(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, dsSite, sampleSizeTable, sampleSizeTableSite, sampleSizeTableTarget, sampleSizeTableAvailable, surveyConsent, consentForValidSurvey", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### surveyBigValues
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, questionsSurveyBigValues, enumeratorID",
                                           names(dset)[stringi::stri_detect_fixed("lev1, questionsSurveyBigValues, enumeratorID", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, questionsSurveyBigValues, enumeratorID", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("surveyBigValues(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, questionsSurveyBigValues, enumeratorID", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### surveyDistinctValues
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, enumeratorID",
                                           names(dset)[stringi::stri_detect_fixed("lev1, enumeratorID", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, enumeratorID", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("surveyDistinctValues(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, enumeratorID", names(dset))]]]<-var1
}
write.csv(var2, paste0("surveyDistinctValues", ".csv"))
```
Please see the generated csv file: surveyDistinctValues.csv
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### surveyMissingValues
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, enumeratorID",
                                           names(dset)[stringi::stri_detect_fixed("lev1, enumeratorID", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, enumeratorID", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("surveyMissingValues(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, enumeratorID", names(dset))]]]<-var1
}
write.csv(var2, paste0("surveyMissingValues", ".csv"))
```
Please see the generated csv file: surveyMissingValues.csv
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### surveyOtherValues
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, otherPattern, enumeratorID",
                                           names(dset)[stringi::stri_detect_fixed("lev1, otherPattern, enumeratorID", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, otherPattern, enumeratorID", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("surveyOtherValues(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, otherPattern, enumeratorID", names(dset))]]]<-var1
}
write.csv(var2, paste0("surveyOtherValues", ".csv"))
```
Please see the generated csv file: surveyOtherValues.csv
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### surveyOutliers
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, enumeratorID",
                                           names(dset)[stringi::stri_detect_fixed("lev1, enumeratorID", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, enumeratorID", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("surveyOutliers(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, enumeratorID", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### surveySmallValues
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, questionsSurveySmallValues, enumeratorID",
                                           names(dset)[stringi::stri_detect_fixed("lev1, questionsSurveySmallValues, enumeratorID", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, questionsSurveySmallValues, enumeratorID", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("surveySmallValues(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, questionsSurveySmallValues, enumeratorID", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### enumeratorIsLazy
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, enumeratorID, questionsEnumeratorIsLazy",
                                           names(dset)[stringi::stri_detect_fixed("lev1, enumeratorID, questionsEnumeratorIsLazy", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, enumeratorID, questionsEnumeratorIsLazy", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("enumeratorIsLazy(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, enumeratorID, questionsEnumeratorIsLazy", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### enumeratorProductivity
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, surveyDate, enumeratorID",
                                           names(dset)[stringi::stri_detect_fixed("lev1, surveyDate, enumeratorID", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, surveyDate, enumeratorID", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("enumeratorProductivity(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, surveyDate, enumeratorID", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### enumeratorProductivityOutliers
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, enumeratorID, surveyDate",
                                           names(dset)[stringi::stri_detect_fixed("lev1, enumeratorID, surveyDate", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, enumeratorID, surveyDate", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("enumeratorProductivityOutliers(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, enumeratorID, surveyDate", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### enumeratorSurveysConsent
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, surveyConsent, enumeratorID",
                                           names(dset)[stringi::stri_detect_fixed("lev1, surveyConsent, enumeratorID", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, surveyConsent, enumeratorID", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("enumeratorSurveysConsent(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, surveyConsent, enumeratorID", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```

### enumeratorSurveysDuration
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, dates, enumeratorID",
                                           names(dset)[stringi::stri_detect_fixed("lev1, dates, enumeratorID", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, dates, enumeratorID", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("enumeratorSurveysDuration(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, dates, enumeratorID", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
```{r eval=TRUE, echo=FALSE, results='asis', fig.align='center'}
if(!is.null(var4)){
  print(var4)
}
```
