---
title: "High Frequency Checks template"
author: "Yannick Pascaud"
date: "`r format(Sys.time(), '%d %B, %Y')`"
always_allow_html: yes
output:
  pdf_document:
    toc: true
    toc_depth: 3
  html_document: default
geometry: margin=0.5in
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(gsubfn)
library(HighFrequencyChecks)
```
```{r eval=TRUE, echo=FALSE}
begin_init_var<-NA
SampleSize<-SampleSize
Header<-sample_dataset
adm<-admin
pts<-SamplePts
#admin<-admin
#df<-sample_dataset
df_site<-"union_name"
df_coord<-c("X_gps_reading_longitude","X_gps_reading_latitude")
admin_site<-"Union"
consent<-"survey_consent"
reportcol<-c("enumerator_id","X_uuid")
buffer<-10
uuid<-"X_uuid"
dates<-c("survey_start","end_survey")
startdate<-"11/11/2018"
mindur<-10
enumid<-"enumerator_id"
otherpattern<-"_other$"
surveydte<-"survey_date"
dteformat<-"%m/%d/%Y"
questions<-c("consent_received.shelter_nfi.non_food_items[.]","consent_received.food_security.main_income[.]","consent_received.child_protection.boy_risk[.]","consent_received.child_protection.girl_risk[.]")
minans<-3
sdvalue<-2
sf_site<-"Union"
sf_target<-"SS"
sf_nbpts<-"TotPts"
formul<-c("done-no-not_eligible-deleted","done-no-not_eligible-deleted-SS")
colorder<-c("site","SS","TotPts","done","not_eligible","no","deleted","yes","final","variance")
```
```{r eval=TRUE, echo=FALSE}
Header$union_name<-tolower(Header$union_name)
```
```{r eval=TRUE, echo=FALSE}
SampleSize$Union<-tolower(SampleSize$Union)
```
```{r eval=TRUE, echo=FALSE}
adm$Union<-tolower(adm$Union)
```

## High Frequency Check - Examples

### 1. Overall checks

#### GIS Checks

check that the recorded site is the actual one
```{r eval=TRUE, echo=FALSE, results='asis'}
list[var1,var2]<-chk1di_GIS_site(adm, Header, df_site, df_coord, admin_site, consent, reportcol, TRUE)
if(!is.null(var1)){
  Header<-var1
}
if(nrow(var2)>0 | !is.null(var2)){
  kable(var2)
} else {
  cat("
no errors")
}
```

check that the survey is done within a **`r buffer`** meter buffer from a sample point
```{r eval=TRUE, echo=FALSE, results='asis'}
list[var1,var2]<-chk1dii_GIS_Xm(pts, Header, df_coord, buffer, consent, reportcol, TRUE)
if(!is.null(var1)){
  Header<-var1
}
if(nrow(var2)>0 | !is.null(var2)){
  kable(var2)
} else {
  cat("
no errors")
}
```

#### Duplicates in unique ID
```{r eval=TRUE, echo=FALSE, results='asis'}
list[var1,var2]<-chk2b_unique_id(Header, uuid, consent, reportcol, TRUE)
if(!is.null(var1)){
  Header<-var1
}
if(nrow(var2)>0 | !is.null(var2)){
  kable(var2)
} else {
  cat("
no errors")
}
```

#### Dates mistakes in the survey

Surveys that do not end on the same day as they started
```{r eval=TRUE, echo=FALSE, results='asis'}
list[var1,var2]<-chk3a_date_mistake(Header, consent, dates, reportcol, FALSE)
if(!is.null(var1)){
  Header<-var1
}
if(nrow(var2)>0 | !is.null(var2)){
  kable(var2)
} else {
  cat("
no errors")
}
```

Surveys which end before they start
```{r eval=TRUE, echo=FALSE, results='asis'}
list[var1,var2]<-chk3b_date_mistake(Header, consent, dates, reportcol, FALSE)
if(!is.null(var1)){
  Header<-var1
}
if(nrow(var2)>0 | !is.null(var2)){
  kable(var2)
} else {
  cat("
no errors")
}
```

Surveys made before the first day of data collection (**`r startdate`**)
```{r eval=TRUE, echo=FALSE, results='asis'}
list[var1,var2]<-chk3c_date_mistake(Header, consent, dates, startdate, reportcol, FALSE)
if(!is.null(var1)){
  Header<-var1
}
if(nrow(var2)>0 | !is.null(var2)){
  kable(var2)
} else {
  cat("
no errors")
}
```

Surveys made in the future
```{r eval=TRUE, echo=FALSE, results='asis'}
list[var1,var2]<-chk3d_date_mistake(Header, consent, dates, reportcol, FALSE)
if(!is.null(var1)){
  Header<-var1
}
if(nrow(var2)>0 | !is.null(var2)){
  kable(var2)
} else {
  cat("
no errors")
}
```

#### Durations of surveys

Beware that surveys with potential errors on the dates are not marked for deletion which can lead to weird durations
```{r eval=TRUE, echo=FALSE, results='asis'}
list[var1,var2]<-chk5a_duration(Header, dates)
if(!is.null(var1)){
  Header<-var1
}
if(nrow(var2)>0 | !is.null(var2)){
  kable(var2)
} else {
  cat("
no errors")
}
```

The total time of data collection is **`r tot`** minutes and the average time per survey is **`r avg`** minutes

Enumerators who made a survey below **`r mindur`** minutes
```{r eval=TRUE, echo=FALSE, results='asis'}
list[var1,var2]<-chk5b_duration_Xmin(Header, consent, dates, reportcol, mindur, TRUE)
if(!is.null(var1)){
  Header<-var1
}
if(nrow(var2)>0 | !is.null(var2)){
  kable(var2)
} else {
  cat("
no errors")
}
```

### 2. Productivity

Number of survey per day of data collection
```{r eval=TRUE, echo=FALSE, results='asis'}
list[var1,var2]<-chk7ai_productivity(Header, surveydte, dteformat, consent)
if(!is.null(var1)){
  Header<-var1
}
if(nrow(var2)>0 | !is.null(var2)){
  kable(var2)
} else {
  cat("
no errors")
}
```

Number of survey per day of data collection per consent status
```{r eval=TRUE, echo=FALSE, results='asis'}
list[var1,var2]<-chk7bi_nb_status(Header, surveydte, dteformat, consent)
if(!is.null(var1)){
  Header<-var1
}
if(nrow(var2)>0 | !is.null(var2)){
  kable(var2)
} else {
  cat("
no errors")
}
```

Tracking sheet
```{r eval=TRUE, echo=FALSE, results='asis'}
list[var1,var2]<-chk7bii_tracking(Header, SampleSize, df_site, sf_site, consent, sf_target, sf_nbpts, formul, colorder)
if(!is.null(var1)){
  Header<-var1
}
if(nrow(var2)>0 | !is.null(var2)){
  kable(var2)
} else {
  cat("
no errors")
}
```

### 3. Checks on the surveys content

#### Number of distinct values per questions
```{r eval=TRUE, echo=FALSE, results='asis'}
list[var1,var2]<-chk4bii_distinct_values(Header, enumid, TRUE)
if(!is.null(var1)){
  Header<-var1
}
write.csv(var2, paste0(chk4bii_distinct_values, ".csv"))
```
Please see the generated csv file: chk4bii_distinct_values.csv

#### Number of other distinct values (for the questions with a possibility of other)
```{r eval=TRUE, echo=FALSE, results='asis'}
list[var1,var2]<-chk4biv_others_values(Header, otherpattern, enumid, TRUE)
if(!is.null(var1)){
  Header<-var1
}
write.csv(var2, paste0(chk4biv_others_values, ".csv"))
```
Please see the generated csv file: chk4biv_others_values.csv

### 4. Enumerators checks

Percentage of survey per consent status by enumerator
```{r eval=TRUE, echo=FALSE, results='asis'}
list[var1,var2]<-chk6a_refusal(Header, consent, enumid)
if(!is.null(var1)){
  Header<-var1
}
if(nrow(var2)>0 | !is.null(var2)){
  kable(var2)
} else {
  cat("
no errors")
}
```

Average interview duration by enumerator
```{r eval=TRUE, echo=FALSE, results='asis'}
list[var1,var2]<-chk6b_duration(Header, dates, enumid)
if(!is.null(var1)){
  Header<-var1
}
if(nrow(var2)>0 | !is.null(var2)){
  kable(var2)
} else {
  cat("
no errors")
}
```

Number of surveys per day by enumerator
```{r eval=TRUE, echo=FALSE, results='asis'}
list[var1,var2]<-chk6c_nb_survey(Header, surveydte, enumid)
if(!is.null(var1)){
  Header<-var1
}
if(nrow(var2)>0 | !is.null(var2)){
  kable(var2)
} else {
  cat("
no errors")
}
```

Surveyors with very low or high productivity
```{r eval=TRUE, echo=FALSE, results='asis'}
list[var1,var2]<-chk6f_productivity(Header, enumid, surveydte, sdvalue)
if(!is.null(var1)){
  Header<-var1
}
if(nrow(var2)>0 | !is.null(var2)){
  kable(var2)
} else {
  cat("
no errors")
}
```

Enumerators who pick up less than **`r minans`** answers per specific questions (Header level)
```{r eval=TRUE, echo=FALSE, results='asis'}
list[var1,var2]<-chk6g_question_less_X_answers(Header, enumid, questions, minans)
if(!is.null(var1)){
  Header<-var1
}
if(nrow(var2)>0 | !is.null(var2)){
  kable(var2)
} else {
  cat("
no errors")
}
```
