---
title: "High Frequency Checks template"
author: "Yannick Pascaud"
date: "`r format(Sys.time(), '%d %B, %Y')`"
always_allow_html: yes
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{High Frequency Checks template}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
geometry: margin=0.5in
fontsize: 10pt
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(knitr)
library(gsubfn)
library(tidyverse)
library(HighFrequencyChecks)
library(geosphere)

# Loads needed datasets
SampleSize <- HighFrequencyChecks::SampleSize
Header <- HighFrequencyChecks::sample_dataset

# Loads needed shapefiles
adm <- HighFrequencyChecks::admin
pts <- HighFrequencyChecks::SamplePts

# correction for uppercase/lowercase in the site name (should not happen if we can use the same name in the shapefile/kobo/sample size)
Header$union_name <- tolower(Header$union_name)
SampleSize$Union <- tolower(SampleSize$Union)
adm$Union <- tolower(adm$Union)

# Initialize common variables
#admin<-admin
#df<-sample_dataset
df_site <- "union_name"
df_coord <- c("X_gps_reading_longitude","X_gps_reading_latitude")
admin_site <- "Union"
consent <- "survey_consent"
reportcol <- c("enumerator_id","X_uuid")
buffer <- 10
uuid <- "X_uuid"
dates <- c("survey_start","end_survey")
startdate <- "11/11/2018"
mindur <- 10
enumid <- "enumerator_id"
otherpattern <- "_other$"
surveydte <- "survey_date"
dteformat <- "%m/%d/%Y"
questions <- c("consent_received.shelter_nfi.non_food_items[.]",
             "consent_received.food_security.main_income[.]",
             "consent_received.child_protection.boy_risk[.]",
             "consent_received.child_protection.girl_risk[.]")
minans <- 3
```

## High Frequency Check - Examples

### 1. Overall checks

#### GIS Checks

check that the recorded site is the actual one

```{r eval=TRUE, echo=TRUE, results='asis'}
list[dts,err] <- chk1di_GIS_site(adm, Header, df_site, df_coord, admin_site, consent, reportcol, TRUE)
Header <- dts

kable(err)
```

check that the survey is done within a **`r buffer`** meter buffer from a sample point

```{r eval=TRUE, echo=TRUE, results='asis'}
list[dts,err] <- chk1dii_GIS_Xm(pts, Header, df_coord, buffer, consent, reportcol, TRUE)
Header <- dts

kable(err)
```

#### Duplicates in unique ID

```{r eval=TRUE, echo=TRUE, results='asis'}
list[dts,err] <- chk2b_unique_id(Header, uuid, consent, reportcol, TRUE)
Header <- dts

kable(err)
```

#### Dates mistakes in the survey

Surveys that do not end on the same day as they started

```{r eval=TRUE, echo=TRUE, results='asis'}
list[dts,err] <- chk3a_date_mistake(Header, consent, dates, reportcol, FALSE)
# Header<-dts

if(nrow(err)>0){
  kable(err)
} else {
  cat("no errors")
}
```

Surveys which end before they start

```{r eval=TRUE, echo=TRUE, results='asis'}
list[dts,err] <- chk3b_date_mistake(Header, consent, dates, reportcol, FALSE)
# Header<-dts

if(nrow(err)>0){
  kable(err)
} else {
  cat("no errors")
}
```

Surveys made before the first day of data collection (**`r startdate`**)

```{r eval=TRUE, echo=TRUE, results='asis'}
list[dts,err] <- chk3c_date_mistake(Header, consent, dates, startdate, reportcol, FALSE)
# Header <- dts
if(nrow(err)>0){
  kable(err)
} else {
  cat("no errors")
}
```

Surveys made in the future

```{r eval=TRUE, echo=TRUE, results='asis'}
list[dts,err] <- chk3d_date_mistake(Header, consent, dates, reportcol, FALSE)
# Header <- dts
if(nrow(err)>0){
  kable(err)
} else {
  cat("no errors")
}
```

#### Durations of surveys

Beware that surveys with potential errors on the dates are not marked for deletion which can lead to weird duration

```{r eval=TRUE, echo=TRUE, results='asis'}
list[avg,tot] <- chk5a_duration(Header, dates)
# Header <- dts
cat("The total time of data collection is", tot, "minutes and the average time per survey is", avg, "minutes")
```

Enumerators who made a survey below **`r mindur`** minutes

```{r eval=TRUE, echo=TRUE, results='asis'}
list[dts,err] <- chk5b_duration_Xmin(Header, consent, dates, reportcol, mindur, TRUE)
Header <- dts
kable(err)
```

### 2. Productivity

Number of survey per day of data collection

```{r eval=TRUE, echo=TRUE, results='asis'}
reportlog <- chk7ai_productivity(Header, surveydte, dteformat, consent)
kable(reportlog)
```

Number of survey per day of data collection per consent status

```{r eval=TRUE, echo=TRUE, results='asis'}
reportlog <- chk7bi_nb_status(Header, surveydte, dteformat, consent)
kable(reportlog)
```

Tracking sheet

```{r eval=TRUE, echo=TRUE, results='asis'}
sf_site="Union"
sf_target="SS"
sf_nbpts="TotPts"
formul=c("done-no-not_eligible-deleted","done-no-not_eligible-deleted-SS")
colorder=c("site","SS","TotPts","done","not_eligible","no","deleted","yes","final","variance")

reportlog <- chk7bii_tracking(Header, SampleSize, df_site, sf_site, consent, sf_target, sf_nbpts, formul, colorder)
kable(reportlog)
```

### 3. Checks on the surveys content

#### Number of distinct values per questions

```{r eval=TRUE, echo=TRUE, results='asis'}
#reportlog <- chk4bii_distinct_values(Header, enumid, TRUE)
#kable(reportlog)
```

\newpage
\blandscape

#### Number of other distinct values (for the questions with a possibility of other)

```{r eval=TRUE, echo=TRUE, results='asis'}
reportlog <- chk4biv_others_values(Header, otherpattern, enumid, TRUE)
kable(reportlog)
```

\elandscape


### 4. Enumerators checks

Percentage of survey per consent status by enumerator

```{r eval=TRUE, echo=TRUE, results='asis'}
reportlog <- chk6a_refusal(Header, consent, enumid)
kable(reportlog)
```

Average interview duration by enumerator

```{r eval=TRUE, echo=TRUE, results='asis'}
reportlog <- chk6b_duration(Header, dates, enumid)
kable(reportlog)
```

Number of surveys per day by enumerator

```{r eval=TRUE, echo=TRUE, results='asis'}
reportlog <- chk6c_nb_survey(Header, surveydte, enumid)
kable(reportlog)
```

Surveyors with very low or high productivity

```{r eval=TRUE, echo=TRUE, results='asis'}
sdvalue=2
reportlog <- chk6f_productivity(Header, enumid, surveydte, sdvalue)
kable(reportlog)
```

Enumerators who pick up less than **`r minans`** answers per specific questions

```{r eval=TRUE, echo=TRUE, results='asis'}
reportlog <- chk6g_question_less_X_answers(Header, enumid, questions, minans)
kable(reportlog)
```

