---
title: "High Frequency Checks template"
author: "Yannick Pascaud"
date: "`r format(Sys.time(), '%d %B, %Y')`"
always_allow_html: yes
output:
  pdf_document:
    toc: true
    toc_depth: 3
  html_document: default
geometry: margin=0.5in
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(gsubfn)
library(dplyr)
library(data.table)
library(HighFrequencyChecks)
```
```{r surveysDataset, eval=TRUE, echo=FALSE}
dset<-list()
dset[["lev1"]]<-sample_dataset
```
```{r sampleSizeDataset, eval=TRUE, echo=FALSE}
begin_sample<-NA
SampleSize<-SampleSize
```
```{r shapefiles, eval=TRUE, echo=FALSE}
begin_shp<-NA
adm<-admin
pts<-SamplePts
```
```{r initializeVariables, eval=TRUE, echo=FALSE}
#Header<-sample_dataset
#admin<-admin
#df<-sample_dataset
df_site<-"union_name"
df_coord<-c("X_gps_reading_longitude","X_gps_reading_latitude")
admin_site<-"Union"
consent<-"survey_consent"
reportcol<-c("enumerator_id","X_uuid")
buffer<-10
uuid<-"X_uuid"
dates<-c("survey_start","end_survey")
startdate<-"11/11/2018"
mindur<-10
enumid<-"enumerator_id"
otherpattern<-"_other$"
surveydte<-"survey_date"
dteformat<-"%m/%d/%Y"
questions_enumeratorIsLazy_level1<-c("consent_received.shelter_nfi.non_food_items[.]","consent_received.food_security.main_income[.]","consent_received.child_protection.boy_risk[.]","consent_received.child_protection.girl_risk[.]")
minans<-3
sdvalue<-2
sf_site<-"Union"
sf_target<-"SS"
sf_nbpts<-"TotPts"
formul<-c("done-no-not_eligible-deleted","done-no-not_eligible-deleted-SS")
colorder<-c("site","SS","TotPts","done","not_eligible","no","deleted","yes","final","variance")
```
```{r eval=TRUE, echo=FALSE}
dset[["lev1"]]$union_name<-tolower(dset[["lev1"]]$union_name)
```
```{r eval=TRUE, echo=FALSE}
SampleSize$Union<-tolower(SampleSize$Union)
```
```{r eval=TRUE, echo=FALSE}
adm$Union<-tolower(adm$Union)
```
```{r eval=TRUE, echo=FALSE}
options(scipen = 999)
```

## High Frequency Check - Examples

### 1. Overall checks

#### GIS Checks

check that the recorded site is the actual one
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("adm, lev1, df_site, df_coord, admin_site, consent, reportcol, TRUE",
                                           names(dset)[stringi::stri_detect_fixed("adm, lev1, df_site, df_coord, admin_site, consent, reportcol, TRUE", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("adm, lev1, df_site, df_coord, admin_site, consent, reportcol, TRUE", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("isInterviewInTheCorrectSite(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("adm, lev1, df_site, df_coord, admin_site, consent, reportcol, TRUE", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```

check that the survey is done within a **`r buffer`** meter buffer from a sample point
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, pts, df_coord, buffer, consent, reportcol, TRUE",
                                           names(dset)[stringi::stri_detect_fixed("lev1, pts, df_coord, buffer, consent, reportcol, TRUE", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, pts, df_coord, buffer, consent, reportcol, TRUE", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("isInterviewAtTheSamplePoint(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, pts, df_coord, buffer, consent, reportcol, TRUE", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```

#### Duplicates in unique ID
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, uuid, consent, reportcol, TRUE",
                                           names(dset)[stringi::stri_detect_fixed("lev1, uuid, consent, reportcol, TRUE", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, uuid, consent, reportcol, TRUE", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("isUniqueIDDuplicated(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, uuid, consent, reportcol, TRUE", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```

#### Dates mistakes in the survey

Surveys that do not end on the same day as they started
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, consent, dates, reportcol, FALSE",
                                           names(dset)[stringi::stri_detect_fixed("lev1, consent, dates, reportcol, FALSE", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, consent, dates, reportcol, FALSE", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("isSurveyOnMoreThanADay(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, consent, dates, reportcol, FALSE", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```

Surveys which end before they start
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, consent, dates, reportcol, FALSE",
                                           names(dset)[stringi::stri_detect_fixed("lev1, consent, dates, reportcol, FALSE", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, consent, dates, reportcol, FALSE", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("isSurveyEndBeforeItStarts(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, consent, dates, reportcol, FALSE", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```

Surveys made before the first day of data collection (**`r startdate`**)
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, dates, consent, startdate, reportcol, FALSE",
                                           names(dset)[stringi::stri_detect_fixed("lev1, dates, consent, startdate, reportcol, FALSE", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, dates, consent, startdate, reportcol, FALSE", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("isSurveyStartedBeforeTheAssessment(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, dates, consent, startdate, reportcol, FALSE", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```

Surveys made in the future
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, consent, dates, reportcol, FALSE",
                                           names(dset)[stringi::stri_detect_fixed("lev1, consent, dates, reportcol, FALSE", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, consent, dates, reportcol, FALSE", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("isSurveyMadeInTheFuture(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, consent, dates, reportcol, FALSE", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```

#### Durations of surveys

Beware that if surveys with potential errors on the dates are not marked for deletion which can lead to weird durations
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, dates",
                                           names(dset)[stringi::stri_detect_fixed("lev1, dates", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, dates", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("assessmentDuration(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, dates", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```

The total time of data collection is **`r var3$tot`** minutes and the average time per survey is **`r var3$avg`** minutes

Enumerators who made a survey below **`r mindur`** minutes
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, consent, dates, reportcol, mindur, TRUE",
                                           names(dset)[stringi::stri_detect_fixed("lev1, consent, dates, reportcol, mindur, TRUE", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, consent, dates, reportcol, mindur, TRUE", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("isInterviewTooShort(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, consent, dates, reportcol, mindur, TRUE", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```

### 2. Productivity

Number of survey per day of data collection
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, surveydte, dteformat, consent",
                                           names(dset)[stringi::stri_detect_fixed("lev1, surveydte, dteformat, consent", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, surveydte, dteformat, consent", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("assessmentProductivity(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, surveydte, dteformat, consent", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```

Number of survey per day of data collection per consent status
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, surveydte, dteformat, consent",
                                           names(dset)[stringi::stri_detect_fixed("lev1, surveydte, dteformat, consent", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, surveydte, dteformat, consent", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("assessmentDailyValidSurveys(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, surveydte, dteformat, consent", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```

Tracking sheet
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, SampleSize, df_site, sf_site, consent, sf_target, sf_nbpts, formul, colorder",
                                           names(dset)[stringi::stri_detect_fixed("lev1, SampleSize, df_site, sf_site, consent, sf_target, sf_nbpts, formul, colorder", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, SampleSize, df_site, sf_site, consent, sf_target, sf_nbpts, formul, colorder", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("assessmentTrackingSheet(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, SampleSize, df_site, sf_site, consent, sf_target, sf_nbpts, formul, colorder", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```

### 3. Checks on the surveys content

#### Number of distinct values per questions
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, enumid, TRUE",
                                           names(dset)[stringi::stri_detect_fixed("lev1, enumid, TRUE", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, enumid, TRUE", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("surveyDistinctValues(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, enumid, TRUE", names(dset))]]]<-var1
}
write.csv(var2, paste0("surveyDistinctValues", ".csv"))
```
Please see the generated csv file: surveyDistinctValues.csv

#### Number of other distinct values (for the questions with a possibility of other)
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, otherpattern, enumid, FALSE",
                                           names(dset)[stringi::stri_detect_fixed("lev1, otherpattern, enumid, FALSE", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, otherpattern, enumid, FALSE", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("surveyOtherValues(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, otherpattern, enumid, FALSE", names(dset))]]]<-var1
}
write.csv(var2, paste0("surveyOtherValues", ".csv"))
```
Please see the generated csv file: surveyOtherValues.csv

### 4. Enumerators checks

Percentage of survey per consent status by enumerator
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, consent, enumid",
                                           names(dset)[stringi::stri_detect_fixed("lev1, consent, enumid", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, consent, enumid", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("enumeratorSurveysConsent(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, consent, enumid", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```

Average interview duration by enumerator
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, dates, enumid",
                                           names(dset)[stringi::stri_detect_fixed("lev1, dates, enumid", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, dates, enumid", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("enumeratorSurveysDuration(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, dates, enumid", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```

Number of surveys per day by enumerator
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, surveydte, enumid",
                                           names(dset)[stringi::stri_detect_fixed("lev1, surveydte, enumid", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, surveydte, enumid", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("enumeratorProductivity(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, surveydte, enumid", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```

Surveyors with very low or high productivity
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, enumid, surveydte, sdvalue",
                                           names(dset)[stringi::stri_detect_fixed("lev1, enumid, surveydte, sdvalue", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, enumid, surveydte, sdvalue", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("enumeratorProductivityOutliers(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, enumid, surveydte, sdvalue", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```

Enumerators who pick up less than **`r minans`** answers per specific questions (Level1 level)
```{r eval=TRUE, echo=FALSE, results='asis'}
tmp<-(stringi::stri_replace_all_fixed("lev1, enumid, questions_enumeratorIsLazy_level1, minans",
                                           names(dset)[stringi::stri_detect_fixed("lev1, enumid, questions_enumeratorIsLazy_level1, minans", names(dset))],
                                           paste0("dset[['", names(dset)[stringi::stri_detect_fixed("lev1, enumid, questions_enumeratorIsLazy_level1, minans", names(dset))], "']]"),
                                           vectorize_all=FALSE))
list[var1,var2,var3,var4]<-eval(parse(text=paste0("enumeratorIsLazy(", tmp, ")")))
if(!is.null(var1)){
  dset[[names(dset)[stringi::stri_detect_fixed("lev1, enumid, questions_enumeratorIsLazy_level1, minans", names(dset))]]]<-var1
}
if(!is.null(var2)){
  if(nrow(var2)>0){
    kable(var2)
  } else {
    cat("
no errors")
  }
}
```
