---
title: "High Frequency Checks template"
always_allow_html: yes
output:
  rmarkdown::html_vignette:
    toc: yes
vignette: >
  \usepackage[utf8]{inputenc}
  %\VignetteIndexEntry{High Frequency Checks template}
  %\VignetteEngine{knitr::rmarkdown}
geometry: margin=0.5in
fontsize: 10pt
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(knitr)
library(gsubfn)
library(dplyr)
library(data.table)
library(HighFrequencyChecks)
options(scipen = 999)
```
```{r define variables, eval=TRUE, echo=FALSE}
ds<-sample_dataset
sampleSizeTable<-SampleSize
adminBoundaries<-admin
sampledPoints<-SamplePts
adminBoundariesSite<-"Union"
buffer<-10
consentForValidSurvey<-"yes"
dateFormat<-"%m/%d/%Y"
dates<-c("survey_start","end_survey")
dsCoordinates<-c("X_gps_reading_longitude","X_gps_reading_latitude")
dsSite<-"union_name"
enumeratorID<-"enumerator_id"
householdSize<-"consent_received.respondent_info.hh_size"
minimumSurveyDuration<-30
minimumSurveyDurationByIndividual<-10
otherPattern<-"_other$"
questionsSurveyBigValues<-c(consent_received.food_security.spend_food=25000,
                            consent_received.food_security.spend_medication=15000,
                            consent_received.food_security.spend_education=10000,
                            consent_received.food_security.spend_fix_shelter=5000,
                            consent_received.food_security.spend_clothing=5000,
                            consent_received.food_security.spend_hygiene=10000,
                            consent_received.food_security.spend_fuel=15000,
                            consent_received.food_security.spend_hh_items=5000,
                            consent_received.food_security.spend_transport=1000,
                            consent_received.food_security.spend_communication=1000, 
                            consent_received.food_security.spend_tobacco=1000,
                            consent_received.food_security.spend_rent=25000,
                            consent_received.food_security.spend_debts=25000,
                            consent_received.food_security.spend_other=25000)
questionsSurveySmallValues<-c(consent_received.food_security.spend_food=400,
                              consent_received.food_security.spend_medication=250,
                              consent_received.food_security.spend_education=400,
                              consent_received.food_security.spend_fix_shelter=300,
                              consent_received.food_security.spend_clothing=200,
                              consent_received.food_security.spend_hygiene=300,
                              consent_received.food_security.spend_fuel=100,
                              consent_received.food_security.spend_hh_items=100,
                              consent_received.food_security.spend_transport=100,
                              consent_received.food_security.spend_communication=100,
                              consent_received.food_security.spend_tobacco=100,
                              consent_received.food_security.spend_rent=300,
                              consent_received.food_security.spend_debts=500,
                              consent_received.food_security.spend_other=500)
questionsEnumeratorIsLazy<-c(consent_received.shelter_nfi.non_food_items=3,
                             consent_received.food_security.main_income=2,
                             consent_received.child_protection.boy_risk=3,
                             consent_received.child_protection.girl_risk=3)
reports<-c("reportisInterviewAtTheSamplePoint", 
           "reportisInterviewCompleted", 
           "reportisInterviewInTheCorrectSite", 
           "reportisInterviewTooShort",
           "reportisInterviewTooShortForTheHouseholdSize", 
           "reportisInterviewWithConsent", 
           "reportisSurveyEndBeforeItStarts", 
           "reportisSurveyMadeInTheFuture", 
           "reportisSurveyOnMoreThanADay",
           "reportisSurveyStartedBeforeTheAssessment", 
           "reportisUniqueIDDuplicated", 
           "reportisUniqueIDMissing")
sampleSizeTableAvailable<-"TotPts"
sampleSizeTableSite<-"Union"
sampleSizeTableTarget<-"SS"
startDataCollection<-"2018-11-11"
surveyConsent<-"survey_consent"
surveyDate<-"survey_date"
uniqueID<-"X_uuid"
deleteIsInterviewCompleted<-TRUE
deleteIsInterviewWithConsent<-TRUE
correctIsInterviewInTheCorrectSite<-TRUE
deleteIsInterviewAtTheSamplePoint<-TRUE
deleteIsUniqueIDMissing<-TRUE
deleteIsUniqueIDDuplicated<-TRUE
deleteIsSurveyOnMoreThanADay<-TRUE
deleteIsSurveyEndBeforeItStarts<-TRUE
deleteIsSurveyStartedBeforeTheAssessment<-TRUE
deleteIsSurveyMadeInTheFuture<-TRUE
deleteIsInterviewTooShort<-TRUE
deleteIsInterviewTooShortForTheHouseholdSize<-TRUE
```
```{r some cleaning, eval=TRUE, echo=FALSE}
ds$union_name<-tolower(ds$union_name)
sampleSizeTable$Union<-tolower(sampleSizeTable$Union)
adminBoundaries$Union<-tolower(adminBoundaries$Union)
```

```{r run all functions, eval=TRUE, echo=FALSE}
list[var1,reportisInterviewCompleted,textisInterviewCompleted,graphisInterviewCompleted] <- 
  isInterviewCompleted(ds=ds, dates=c("survey_start","end_survey"), surveyConsent="survey_consent", deleteIsInterviewCompleted=TRUE)
if(!is.null(var1)){
  ds<-var1
}
list[var1,reportisInterviewWithConsent,textisInterviewWithConsent,graphisInterviewWithConsent] <- 
  isInterviewWithConsent(ds=ds, surveyConsent="survey_consent", deleteIsInterviewWithConsent=TRUE)
if(!is.null(var1)){
  ds<-var1
}
list[var1,reportisInterviewInTheCorrectSite,textisInterviewInTheCorrectSite,graphisInterviewInTheCorrectSite] <- 
  isInterviewInTheCorrectSite(ds=ds, adminBoundaries=adminBoundaries, adminBoundariesSite="Union", dsCoordinates=c("X_gps_reading_longitude","X_gps_reading_latitude"), dsSite="union_name", surveyConsent="survey_consent", correctIsInterviewInTheCorrectSite=TRUE)
if(!is.null(var1)){
  ds<-var1
}
list[var1,reportisInterviewAtTheSamplePoint,textisInterviewAtTheSamplePoint,graphisInterviewAtTheSamplePoint] <- 
  isInterviewAtTheSamplePoint(ds=ds, sampledPoints=sampledPoints, buffer=10, dsCoordinates=c("X_gps_reading_longitude","X_gps_reading_latitude"), surveyConsent="survey_consent", deleteIsInterviewAtTheSamplePoint=TRUE)
if(!is.null(var1)){
  ds<-var1
}
list[var1,reportisUniqueIDMissing,textisUniqueIDMissing,graphisUniqueIDMissing] <- 
  isUniqueIDMissing(ds=ds, surveyConsent="survey_consent", uniqueID="X_uuid", deleteIsUniqueIDMissing=TRUE)
if(!is.null(var1)){
  ds<-var1
}
list[var1,reportisUniqueIDDuplicated,textisUniqueIDDuplicated,graphisUniqueIDDuplicated] <- 
  isUniqueIDDuplicated(ds=ds, surveyConsent="survey_consent", uniqueID="X_uuid", deleteIsUniqueIDDuplicated=TRUE)
if(!is.null(var1)){
  ds<-var1
}
list[var1,reportisSurveyOnMoreThanADay,textisSurveyOnMoreThanADay,graphisSurveyOnMoreThanADay] <- 
  isSurveyOnMoreThanADay(ds=ds, dates=c("survey_start","end_survey"), surveyConsent="survey_consent", deleteIsSurveyOnMoreThanADay=TRUE)
if(!is.null(var1)){
  ds<-var1
}
list[var1,reportisSurveyEndBeforeItStarts,textisSurveyEndBeforeItStarts,graphisSurveyEndBeforeItStarts] <- 
  isSurveyEndBeforeItStarts(ds=ds, dates=c("survey_start","end_survey"), surveyConsent="survey_consent", deleteIsSurveyEndBeforeItStarts=TRUE)
if(!is.null(var1)){
  ds<-var1
}
list[var1,reportisSurveyStartedBeforeTheAssessment,textisSurveyStartedBeforeTheAssessment,graphisSurveyStartedBeforeTheAssessment] <- 
  isSurveyStartedBeforeTheAssessment(ds=ds, dates=c("survey_start","end_survey"), startDataCollection="2018-11-11", surveyConsent="survey_consent", deleteIsSurveyStartedBeforeTheAssessment=TRUE)
if(!is.null(var1)){
  ds<-var1
}
list[var1,reportisSurveyMadeInTheFuture,textisSurveyMadeInTheFuture,graphisSurveyMadeInTheFuture] <- 
  isSurveyMadeInTheFuture(ds=ds, dates=c("survey_start","end_survey"), surveyConsent="survey_consent", deleteIsSurveyMadeInTheFuture=TRUE)
if(!is.null(var1)){
  ds<-var1
}
list[var1,reportisInterviewTooShort,textisInterviewTooShort,graphisInterviewTooShort] <- 
  isInterviewTooShort(ds=ds, dates=c("survey_start","end_survey"), minimumSurveyDuration=30, surveyConsent="survey_consent", deleteIsInterviewTooShort=TRUE)
if(!is.null(var1)){
  ds<-var1
}
list[var1,reportisInterviewTooShortForTheHouseholdSize,textisInterviewTooShortForTheHouseholdSize,graphisInterviewTooShortForTheHouseholdSize] <- 
  isInterviewTooShortForTheHouseholdSize(ds=ds, dates=c("survey_start","end_survey"), householdSize="consent_received.respondent_info.hh_size", minimumSurveyDurationByIndividual=10, surveyConsent="survey_consent", deleteIsInterviewTooShortForTheHouseholdSize=TRUE)
if(!is.null(var1)){
  ds<-var1
}

list[var1,reportassessmentDuration,textassessmentDuration,graphassessmentDuration] <- 
  assessmentDuration(ds=ds, dates=c("survey_start","end_survey"))
list[var1,reportassessmentDurationOutliers,textassessmentDurationOutliers,graphassessmentDurationOutliers] <- 
  assessmentDurationOutliers(ds=ds, dates=c("survey_start","end_survey"))
list[var1,reportassessmentProductivity,textassessmentProductivity,graphassessmentProductivity] <- 
  assessmentProductivity(ds=ds, dateFormat="%m/%d/%Y", surveyConsent="survey_consent", surveyDate="survey_date")
list[var1,reportassessmentDailyValidSurveys,textassessmentDailyValidSurveys,graphassessmentDailyValidSurveys] <- 
  assessmentDailyValidSurveys(ds=ds, dateFormat="%m/%d/%Y", surveyConsent="survey_consent", surveyDate="survey_date")
list[var1,reportassessmentTrackingSheet,textassessmentTrackingSheet,graphassessmentTrackingSheet] <- 
  assessmentTrackingSheet(ds=ds, sampleSizeTable=sampleSizeTable, consentForValidSurvey="yes", dsSite="union_name", sampleSizeTableAvailable="TotPts", sampleSizeTableSite="Union", sampleSizeTableTarget="SS", surveyConsent="survey_consent")

list[var1,reportsurveyMissingValues,textsurveyMissingValues,graphsurveyMissingValues] <- 
  surveyMissingValues(ds=ds, enumeratorID="enumerator_id")
list[var1,reportsurveyDistinctValues,textsurveyDistinctValues,graphsurveyDistinctValues] <- 
  surveyDistinctValues(ds=ds, enumeratorID="enumerator_id")
list[var1,reportsurveyOtherValues,textsurveyOtherValues,graphsurveyOtherValues] <- 
  surveyOtherValues(ds=ds, enumeratorID="enumerator_id", otherPattern="_other$")
list[var1,reportsurveyOutliers,textsurveyOutliers,graphsurveyOutliers] <- 
  surveyOutliers(ds=ds, enumeratorID="enumerator_id")
list[var1,reportsurveySmallValues,textsurveySmallValues,graphsurveySmallValues] <- 
  surveySmallValues(ds=ds, enumeratorID="enumerator_id", questionsSurveySmallValues=c(consent_received.food_security.spend_food=400,
                                                                                      consent_received.food_security.spend_medication=250,
                                                                                      consent_received.food_security.spend_education=400,
                                                                                      consent_received.food_security.spend_fix_shelter=300,
                                                                                      consent_received.food_security.spend_clothing=200,
                                                                                      consent_received.food_security.spend_hygiene=300,
                                                                                      consent_received.food_security.spend_fuel=100,
                                                                                      consent_received.food_security.spend_hh_items=100,
                                                                                      consent_received.food_security.spend_transport=100,
                                                                                      consent_received.food_security.spend_communication=100,
                                                                                      consent_received.food_security.spend_tobacco=100,
                                                                                      consent_received.food_security.spend_rent=300,
                                                                                      consent_received.food_security.spend_debts=500,
                                                                                      consent_received.food_security.spend_other=500))
list[var1,reportsurveyBigValues,textsurveyBigValues,graphsurveyBigValues] <- 
  surveyBigValues(ds=ds, enumeratorID="enumerator_id", questionsSurveyBigValues=c(consent_received.food_security.spend_food=25000,
                                                                                  consent_received.food_security.spend_medication=15000,
                                                                                  consent_received.food_security.spend_education=10000,
                                                                                  consent_received.food_security.spend_fix_shelter=5000,
                                                                                  consent_received.food_security.spend_clothing=5000,
                                                                                  consent_received.food_security.spend_hygiene=10000,
                                                                                  consent_received.food_security.spend_fuel=15000,
                                                                                  consent_received.food_security.spend_hh_items=5000,
                                                                                  consent_received.food_security.spend_transport=1000,
                                                                                  consent_received.food_security.spend_communication=1000, 
                                                                                  consent_received.food_security.spend_tobacco=1000,
                                                                                  consent_received.food_security.spend_rent=25000,
                                                                                  consent_received.food_security.spend_debts=25000,
                                                                                  consent_received.food_security.spend_other=25000))

list[var1,reportenumeratorSurveysConsent,textenumeratorSurveysConsent,graphenumeratorSurveysConsent] <- 
  enumeratorSurveysConsent(ds=ds, enumeratorID="enumerator_id", surveyConsent="survey_consent")
list[var1,reportenumeratorSurveysDuration,textenumeratorSurveysDuration,graphenumeratorSurveysDuration] <- 
  enumeratorSurveysDuration(ds=ds, dates=c("survey_start","end_survey"), enumeratorID="enumerator_id")
list[var1,reportenumeratorProductivity,textenumeratorProductivity,graphenumeratorProductivity] <- 
  enumeratorProductivity(ds=ds, enumeratorID="enumerator_id", surveyDate="survey_date")
list[var1,reportenumeratorProductivityOutliers,textenumeratorProductivityOutliers,graphenumeratorProductivityOutliers] <- 
  enumeratorProductivityOutliers(ds=ds, enumeratorID="enumerator_id", surveyDate="survey_date")
list[var1,reportenumeratorIsLazy,textenumeratorIsLazy,graphenumeratorIsLazy] <- 
  enumeratorIsLazy(ds=ds, enumeratorID="enumerator_id", questionsEnumeratorIsLazy=c(consent_received.shelter_nfi.non_food_items=3,
                                                                                    consent_received.food_security.main_income=2,
                                                                                    consent_received.child_protection.boy_risk=3,
                                                                                    consent_received.child_protection.girl_risk=3))
list[var1,reportenumeratorErrorsDashboard,textenumeratorErrorsDashboard,graphenumeratorErrorsDashboard] <- 
  enumeratorErrorsDashboard(enumeratorID="enumerator_id", reports=c("reportisInterviewAtTheSamplePoint", 
                                                                    "reportisInterviewCompleted", 
                                                                    "reportisInterviewInTheCorrectSite", 
                                                                    "reportisInterviewTooShort",
                                                                    "reportisInterviewTooShortForTheHouseholdSize", 
                                                                    "reportisInterviewWithConsent", 
                                                                    "reportisSurveyEndBeforeItStarts", 
                                                                    "reportisSurveyMadeInTheFuture", 
                                                                    "reportisSurveyOnMoreThanADay",
                                                                    "reportisSurveyStartedBeforeTheAssessment", 
                                                                    "reportisUniqueIDDuplicated", 
                                                                    "reportisUniqueIDMissing"))
```

## Summary of defined parameters

```{r display summaryParameters, eval=TRUE, echo=FALSE, results='asis'}
if(!is.null(buffer) | !is.na(buffer) | buffer!=""){
  cat(paste0("The buffer for the points to be valid is set to ", buffer, " meters from the sampled point  \n"))
}
if(!is.null(minimumSurveyDuration) | !is.na(minimumSurveyDuration) | minimumSurveyDuration!=""){
  cat(paste0("The minimum duration for a survey to be valid is set to ", minimumSurveyDuration, " minutes  \n"))
}
if(!is.null(minimumSurveyDurationByIndividual) | !is.na(minimumSurveyDurationByIndividual) | minimumSurveyDurationByIndividual!=""){
  cat(paste0("The minimum duration taken into account the household size (duration per individual) for a survey to be valid is set to ", minimumSurveyDurationByIndividual, " minutes  \n"))
}
kable(data.frame(Values=questionsSurveySmallValues), caption = "Questions with values under will be reported for further checking", format = "html") %>%
  kableExtra::kable_styling(full_width=T)
kable(data.frame(Values=questionsSurveyBigValues), caption = "Questions with values above will be reported for further checking", format = "html") %>%
  kableExtra::kable_styling(full_width=T)
kable(data.frame(minimumAnswers=questionsEnumeratorIsLazy), caption = "Questions with an expected minimum number of answers", format = "html") %>%
  kableExtra::kable_styling(full_width=T)
```

## Overall duration of the assessment till now

```{r display textassessmentDuration, eval=TRUE, echo=FALSE, results='asis', fig.align='center', fig.width=10, fig.height=8}
if(!is.null(textassessmentDuration)){
  cat(textassessmentDuration)
}
```

## Reports

```{r export results in csv, eval=TRUE, echo=FALSE, results='asis'}
listReports <- data.frame(Reports=character(), stringsAsFactors = FALSE)
for(i in ls(all.names = T)[ls(all.names = T) %like% "report"]){
  if(i=="reports"){
    #Do nothing
  } else{
    write.csv(get(i), paste0(i, ".csv"))
    listReports <- rbind(listReports, data.frame(Reports=i), stringsAsFactors = FALSE)
  }
}
cat("The following reports have been exported in .csv for further analysis or to prepare the cleaning log")
kable(listReports, caption = "Reports list", format = "html") %>%
  kableExtra::kable_styling(full_width=T)
```

## Overview of errors which should lead to a survey deletion

```{r display graphi, eval=TRUE, echo=FALSE, results='asis', fig.align='center', fig.width=10, fig.height=8}
colors <- c("OK" = "#238b45", "NOK" = "#cb181d")
for(i in ls(all.names = T)[ls(all.names = T) %like% "graphi"]){
  eval(parse(text=paste0(i, " <- ", i, " + ggplot2::theme(plot.title=ggplot2::element_text(size=10), plot.subtitle=ggplot2::element_text(size=8, colour = ' red')) + ggplot2::scale_fill_manual(values = colors)")))
}
gridExtra::grid.arrange(grobs=mget(ls(all.names = T)[ls(all.names = T) %like% "graphi"]), ncol = 4)
```

## Assessment follow-up

```{r display grapha, eval=FALSE, echo=FALSE, results='asis', fig.align='center', fig.width=10, fig.height=6}
for(i in ls(all.names = T)[ls(all.names = T) %like% "grapha"]){
  if(!is.null(get(i))){
    print(get(i) + ggplot2::labs(title=i))
  }
}
```

### Productivity

```{r display graphassessmentProductivity, eval=TRUE, echo=FALSE, results='asis', fig.align='center', fig.width=10, fig.height=6}
print(graphassessmentProductivity)
```

### Daily surveys by status

```{r display graphassessmentDailyValidSurveys, eval=TRUE, echo=FALSE, results='asis', fig.align='center', fig.width=10, fig.height=6}
colors <- eval(parse(text=paste0("c(", paste0(unique(ds$survey_consent), "='", colormap::colormap(colormap=c('#fff5f0','#67000d'), nshades=length(unique(ds$survey_consent))), "'", collapse = ","), ")")))
colors["yes"] <- "#238b45"

print(graphassessmentDailyValidSurveys + ggplot2::theme(legend.position = 'bottom') + 
        ggplot2::scale_fill_manual(values = colors))
```

### Surveys duration outliers

```{r display graphassessmentDurationOutliers, eval=TRUE, echo=FALSE, results='asis', fig.align='center', fig.width=10, fig.height=1.5}
print(graphassessmentDurationOutliers)
```

### Tracking Sheet

```{r display graphassessmentTrackingSheet, eval=TRUE, echo=FALSE, results='asis', fig.align='center', fig.width=10, fig.height=6}
print(graphassessmentTrackingSheet + ggplot2::theme(legend.position = 'bottom'))
if(!is.null(textassessmentTrackingSheet)){
  cat(textassessmentTrackingSheet)
}
```

<!-- ## Graph s -->
<!-- s functions do not generate graphs -->

## Enumerators follow-up

### Productivity

```{r display graphenumeratorProductivity, eval=TRUE, echo=FALSE, results='asis', fig.align='center', fig.width=10, fig.height=10}
print(graphenumeratorProductivity)
```

### Productivity outliers

```{r display graphenumeratorProductivityOutliers, eval=TRUE, echo=FALSE, results='asis', fig.align='center', fig.width=10, fig.height=1.5}
print(graphenumeratorProductivityOutliers)
```

### Percentage of valid surveys

```{r display graphenumeratorSurveysConsent, eval=TRUE, echo=FALSE, results='asis', fig.align='center', fig.width=10, fig.height=10}
colors <- eval(parse(text=paste0("c(", paste0(unique(ds$survey_consent), "='", colormap::colormap(colormap=c('#fff5f0','#67000d'), nshades=length(unique(ds$survey_consent))), "'", collapse = ","), ")")))
colors["yes"] <- "#238b45"

print(graphenumeratorSurveysConsent + ggplot2::theme(legend.position = 'bottom') + 
        ggplot2::scale_fill_manual(values = colors))
```

### Surveys duration

```{r display graphenumeratorSurveysDuration, eval=TRUE, echo=FALSE, results='asis', fig.align='center', fig.width=10, fig.height=10}
print(graphenumeratorSurveysDuration)
```

### Overall number of errors per type by enumerator

```{r display graph enumeratorErrorsDashboard, eval=TRUE, echo=FALSE, results='asis', fig.align='center', fig.width=10, fig.height=30}
print(graphenumeratorErrorsDashboard)
```


